Effect of quality-adjusted production function inputs

### 2015-05-05 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now using leaf_apply for fitted data.

@@

>>>>

<<Fitted_Data>>=
  extract_fitted_comparison <- function(mod, id){
    df <- mod$data[ , c("Year", "iGDP", "Country")]
    # Trim fitted to be same length as df to eliminate problems with possible NAs at end of fitted
    df$fitted <- yhat(mod)[c(1:length(df$Year))]
    # Parse the id to find out whether this is quality-adjusted data
    id_list <- strsplit(id, split = "[.]")[[1]]
    if (id_list[[2]] == "unadj"){
      df$adjusted <- "Unadjusted"
    } else if (id_list[[2]] == "adj"){
      df$adjusted <- "Quality-adjusted"
    } else {
      stop("Unknown adjustment.")
    }
    if (id_list[[3]] == "noE"){
      df$energy <- "Without energy"
    } else if (id_list[[3]] == "withE"){
      df$energy <- "With energy"
    } else {
      stop("Unknown energy.")
    }
    df$model <- id_list[[4]]    
    return(df)
  }
  fitted_data <- leaf_apply(models, extract_fitted_comparison, class=c("CDEmodel", "cesEst", "LINEXmodel"))
  fitted_data <- do.call(rbind, fitted_data)
@

@@

Now, let's compare the fits to historical data.
